Interisland movements of woodland caribou in Newfoundland

### 2020-02-17 paper/manuscript.Rmd
fix yaml author

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
header-includes:  ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland^2^; Department of Biology, Memorial University of Newfoundland, Canada.

output: 
    #word_document
    github_document
---

>>>>

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date:  ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland; ^2^ Department of Biology, Memorial University of Newfoundland, Canada.
output: 
    #word_document
    github_document
---
